Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-07-24 paper-correlations.tex
Insert an image of balls
Add SEM images and more

\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs,nofootinbib]{revtex4-1}
% Latex
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% Xelatex
%\usepackage{polyglossia}
%\usepackage{fontspec}
%\setdefaultlanguage{english}
%\setmainfont{DejaVu Sans}
%\setsansfont{DejaVu Sans}
%\setmonofont{DejaVu Sans Mono}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}

@@

\subsection{Comparison against analytical solutions}
To test out package we generate a realization of random overlapping disks
(\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
parameters $R = 40\ px$ and $\lambda = 10^{-4}\ px^{-2}$ and compare calculated
correlation functions with their theoretical values.
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\linewidth]{images/disks-fragment.png}
  \caption[]{A fragment of overlapping disks used in testing of our library.}
  \label{fig:overlapping-disks}
\end{figure}

@@

\subsection{Examples of application to experimental images}
\label{sec:examples}
A summary which contains information about type of the images, dimensions and resolution
can be found in \cref{tab:samples}. XCT images of sandstones are provided by
Digital Rocks Portal\cite{DigitalRocks}. Correlation functions of XCT images
can be seen on \cref{fig:real-xct}.

\begin{table*}[!pt]
  \centering
  \begin{ruledtabular}
    \begin{tabular}{|c|c|c|c|}
      Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) \\
      \hline
      Castlegate sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Bentheimer sandstone & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Kirby sandstone      & XCT & $1000 \times 1000 \times 1000$ & 2.25 \\
      Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 \\
      Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 \\
      Carbonate 1 & SEM &  $1024 \times 691$ & 0.06
    \end{tabular}
  \end{ruledtabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:samples}
\end{table*}

\begin{figure*}[pt]
  \centering
  \subfigure[Castlegate sandstone]{
    \includegraphics[width=0.3\linewidth]{samples/CastleGate_2d25um_binary.png}
    \label{fig:castlegate}}
  \hfill
  \subfigure[Bentheimer sandstone]{
    \includegraphics[width=0.3\linewidth]{samples/Bentheimer_2d25um_binary.png}
    \label{fig:bentheimer}}
  \hfill
  \subfigure[Kirby sandstone]{
    \includegraphics[width=0.3\linewidth]{samples/Kirby_2d25um_binary.png}
    \label{fig:kirby}}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/s2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/c2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/l2-xct.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/surf2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/surfvoid-xct.png}
  \caption[]{Visualization of XCT images and plots of correlation functions for
    these images.}
  \label{fig:real-xct}
\end{figure*}

@@

% Replace by two disks?
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.6\linewidth]{images/timing-image.png}
  \caption[]{One of 2D image used in timing measurements.}
  \label{fig:valuenoise}
\end{figure}

>>>>

\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs,nofootinbib]{revtex4-1}
% Latex
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% Xelatex
%\usepackage{polyglossia}
%\usepackage{fontspec}
%\setdefaultlanguage{english}
%\setmainfont{DejaVu Sans}
%\setsansfont{DejaVu Sans}
%\setmonofont{DejaVu Sans Mono}
\usepackage{bm}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[export]{adjustbox}

@@

\subsection{Comparison against analytical solutions}
To test out package we generate a realization of random overlapping disks
(\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
parameters $R = 40\ px$ and $\lambda = 10^{-4}\ px^{-2}$ and compare calculated
correlation functions with their theoretical values.
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.45\linewidth]{images/disks.png}
  \includegraphics[width=0.45\linewidth]{images/balls.png}
  \caption[]{Images of overlapping disks and balls used in testing of our library.}
  \label{fig:overlapping-disks}
\end{figure}

@@

\subsection{Examples of application to experimental images}
\label{sec:examples}
A summary which contains information about type of the images, dimensions and resolution
can be found in \cref{tab:samples}. Correlation functions of XCT images can be
seen on \cref{fig:real-xct} and correlation functions of SEM images are on
\cref{fig:real-sem}.

\begin{table*}[!pt]
  \centering
  \begin{ruledtabular}
    \begin{tabular}{|c|c|c|c|c|}
      Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
      \hline
      Ceramic 1   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9823 \\
      Ceramic 2   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9890 \\
      Ceramic 3   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9712 \\
      Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
      Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 & 0.9897 \\
      Carbonate 1 & SEM &  $1024 \times 691$ & 0.06 & 0.9721
    \end{tabular}
  \end{ruledtabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:samples}
\end{table*}

\begin{figure*}[pt]
  \centering
  \subfigure[Ceramic 1]{
    \includegraphics[width=0.3\linewidth]{samples/Ceramic1.png}}
  \hfill
  \subfigure[Ceramic 2]{
    \includegraphics[width=0.3\linewidth]{samples/Ceramic2.png}}
  \hfill
  \subfigure[Ceramic 3]{
    \includegraphics[width=0.3\linewidth]{samples/Ceramic3.png}}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/s2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/c2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/l2-xct.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/surf2-xct.png}
  \includegraphics[width=0.3\linewidth]{samples/surfvoid-xct.png}
  \caption[]{Visualization of XCT images and plots of correlation functions for
    these images.}
  \label{fig:real-xct}
\end{figure*}

\begin{figure*}[pt]
  \centering
  \subfigure[Sandstone 1]{
    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone1.png}}
  \hfill
  \subfigure[Sandstone 2]{
    \includegraphics[width=0.3\linewidth, frame]{samples/sandstone2.png}}
  \hfill
  \subfigure[Carbonate 1]{
    \includegraphics[width=0.3\linewidth, frame]{samples/carbonate1.png}}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/s2-sem.png}
  \includegraphics[width=0.3\linewidth]{samples/c2-sem.png}
  \includegraphics[width=0.3\linewidth]{samples/l2-sem.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{samples/surf2-sem.png}
  \includegraphics[width=0.3\linewidth]{samples/surfvoid-sem.png}
  \caption[]{SEM images and plots of correlation functions for these images.}
  \label{fig:real-sem}
\end{figure*}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.6\linewidth]{images/timing-image.png}
  \caption[]{One of 2D image used in timing measurements.}
  \label{fig:valuenoise}
\end{figure}
